\dnest~Manual

### 2016-01-14 doc/manual.tex
DNest3 mentions changed to DNest4
GalaxyField example

\begin{figure}
\begin{framed}
\begin{verbatim}
DNest4 Command Line Options: 
-h: display this message
-o <filename>: load DNest3 options from the specified file. Default=OPTIONS
-s <seed>: seed the random number generator with the specified value. If unspecified, the system time is used.
-d <filename>: Load data from the specified file, if required.
-c <value>: Specify a compression value (between levels) other than e.
-t <num_threads>: run on the specified number of threads. Default=1.
\end{verbatim}
\end{framed}
\end{figure}

@@

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine, and
RJObject\_SineWaves. It also contains an empty Template example which you can use
to implement your own models.\\

>>>>

\begin{figure}
\begin{framed}
\begin{verbatim}
DNest4 Command Line Options: 
-h: display this message
-o <filename>: load DNest4 options from the specified file. Default=OPTIONS
-s <seed>: seed the random number generator with the specified value. If unspecified, the system time is used.
-d <filename>: Load data from the specified file, if required.
-c <value>: Specify a compression value (between levels) other than e.
-t <num_threads>: run on the specified number of threads. Default=1.
\end{verbatim}
\end{framed}
\end{figure}

@@

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine,
RJObject\_SineWaves, and RJObject\_GalaxyField.
It also contains an empty Template example which you can use
to implement your own models.\\
